\subsubsection{fusesoc\_info Targets}
\begin{itemize}
\item default
	\begin{itemize}
	\item[$\space$] Info: Default for IP intergration.
	\end{itemize}
\item sim
	\begin{itemize}
	\item[$\space$] Info: Test 1:1 conversion.
	\end{itemize}
\item sim\_reduce
	\begin{itemize}
	\item[$\space$] Info: Test data reduction.
	\end{itemize}
\item sim\_rand\_data\_reduce
	\begin{itemize}
	\item[$\space$] Info: Test data reduction with random data
	\end{itemize}
\item sim\_rand\_ready\_rand\_data\_reduce
	\begin{itemize}
	\item[$\space$] Info: Test data reduction with random ready and random data.
	\end{itemize}
\item sim\_8bit\_count\_data\_reduce
	\begin{itemize}
	\item[$\space$] Info: Test data reduction with counter data.
	\end{itemize}
\item sim\_rand\_ready\_8bit\_count\_data\_reduce
	\begin{itemize}
	\item[$\space$] Info: Test data reduction with counter data, and random ready.
	\end{itemize}
\item sim\_increase
	\begin{itemize}
	\item[$\space$] Info: Test data increase.
	\end{itemize}
\item sim\_rand\_data\_increase
	\begin{itemize}
	\item[$\space$] Info: Test data increase with random data.
	\end{itemize}
\item sim\_rand\_ready\_rand\_data\_increase
	\begin{itemize}
	\item[$\space$] Info: Test data increase with random data, and random ready.
	\end{itemize}
\item sim\_8bit\_count\_data\_increase
	\begin{itemize}
	\item[$\space$] Info: Test data increase with count data.
	\end{itemize}
\item sim\_rand\_ready\_8bit\_count\_data\_increase
	\begin{itemize}
	\item[$\space$] Info: Test data increase with count data, and random ready.
	\end{itemize}
\end{itemize}
